Probability of causal contact between interstellar civilizations through MonteCarlo simulations

### 2019-08-08 manuscript.tex
analisis del waiting time

\setlength{\tabcolsep}{10pt}
\begin{table*}
\centering
\begin{tabular}{cccccc}
\hline
Model subset & D$_{max}$ & $\tau_a$ & $\tau_s$ & size & description  \\
M1 & $<$5000 & $<$15000 & $<$15000 &800  &dense awakening and short lifetime\\
M2 & $<$5000 & $>$20000 & $>$50000 &1050 &sparse awakening and long lifetime\\
M3 & $<$5000 & $<$5000  & $>$15000 &1350 &dense awakening and long lifetime \\
M4 & $<$5000 & $>$15000 & $<$26000 &1200 &sparse awakening and short lifetime\\

M5 & $>$20000 & $<$15000 & $<$15000 &800  &dense awakening and short lifetime\\
M6 & $>$20000 & $>$20000 & $>$50000 &1050 &sparse awakening and long lifetime\\
M7 & $>$20000 & $<$5000  & $>$15000 &1350 &dense awakening and long lifetime \\
M8 & $>$20000 & $>$15000 & $<$26000 &1200 &sparse awakening and short lifetime\\
\hline
\end{tabular}
\caption{Selected models to analize the behevior of some variables.}
\label{T_SelectedModels}
\end{table*}

\begin{figure} \centering
   %
   \includegraphics[width=0.5\textwidth]{Figure_1.png}
   %
   \caption{Empirical cumulative distributions of the number contacts
   for CETIs in four different samplas (M5, M6, M7, M8) with long
   range signal reach (D$_{max}$=10000).
   %
   }
   % 
\label{F_res_1} \end{figure}

\begin{figure} % Distribution
   \centering
   \includegraphics[width=0.5\textwidth]{Figure_2.png}
   \caption{Rate of CETIs that make no contact as a function of
   $\tau_a$ and $\tau_s$}
   \label{F_res_2}
\end{figure}

\begin{figure}
   \centering
   \includegraphics[width=0.5\textwidth]{Figure_3.png}
   \caption{Distribution of number of contacts as a function of
   galactocentric distance.}
   \label{F_res_5}
\end{figure}

\begin{figure} % 2D color plot
   \centering
   \includegraphics[width=0.5\textwidth]{Figure_4.png}
   \caption{}
   \label{F_res_4}
\end{figure}

 \begin{figure} % 2D color plot
   \centering
   \includegraphics[width=0.5\textwidth]{Figure_5.png}
   \caption{Rate of CETIs that listen at least one time, and make its
   first contact at the moment of the awakening, as a funcion of
   $\tau_a$ and $\tau_s$}
   \label{F_res_3}
\end{figure}

@@

>>>>

\setlength{\tabcolsep}{10pt}
\begin{table*}
\centering
\begin{tabular}{ccccc}
\hline
Model subset & D$_{max}$ & $\tau_a$ & $\tau_s$ & description  \\
\hline
M1 & 40000 & [10000, 30000]   & [10000, 50000]   &dense, short lifetime\\
M2 & 40000 & [170000, 190000] & [10000, 50000]   &sparse, short lifetime\\
M3 & 40000 & [10000, 30000]   & [400000, 440000] &dense, long lifetime \\
M4 & 40000 & [170000, 190000] & [400000, 440000] &sparse, long lifetime\\

M5 & 80000 & [10000, 30000]   & [10000, 50000]   &dense, short lifetime\\
M6 & 80000 & [170000, 190000] & [10000, 50000]   &sparse, short lifetime\\
M7 & 80000 & [10000, 30000]   & [400000, 440000] &dense, long lifetime \\
M8 & 80000 & [170000, 190000] & [400000, 440000] &sparse, long lifetime\\

\hline
\end{tabular}
\caption{Selected models to analize the behevior of some variables.}
\label{T_SelectedModels}
\end{table*}

\begin{figure} \centering
   %
   \includegraphics[width=0.5\textwidth]{F1.pdf}
   %
   \caption{Empirical cumulative distributions of the number contacts
   for CETIs in four different samplas (M5, M6, M7, M8) with long
   range signal reach (D$_{max}$=10000).
   %
   }
   % 
\label{F_res_1} \end{figure}

\begin{figure} % Distribution
   \centering
   \includegraphics[width=0.5\textwidth]{F2.pdf}
   \caption{Rate of CETIs that make no contact as a function of
   $\tau_a$ and $\tau_s$}
   \label{F_res_2}
\end{figure}

\begin{figure*} % 2D color plot
   \centering
   \includegraphics[width=0.3\textwidth]{m1d2.png}%
   \includegraphics[width=0.3\textwidth]{m1d3.png}%
   \includegraphics[width=0.3\textwidth]{m1d4.png}
   \caption{Rate of CETIs that never make contact (listening) as a
   function of $\tau_a$ and $\tau_s$, for 
   $D_{max}$=10000 (left panel),
   $D_{max}$=40000 (middle panel), and
   $D_{max}$=80000 (right panel)}
   \label{F_res_3}
\end{figure*}

\begin{figure*} % 2D color plot
   \centering
   \includegraphics[width=0.3\textwidth]{m2d2.png}%
   \includegraphics[width=0.3\textwidth]{m2d3.png}%
   \includegraphics[width=0.3\textwidth]{m2d4.png}
   \caption{Rate of CETIs that listen at the moment of the
   awakening, as a funcion of $\tau_a$ and $\tau_s$}
   \label{F_res_4}
\end{figure*}

\begin{figure}
   \centering
   \includegraphics[width=0.5\textwidth]{radial.png}
   \caption{Fraction of CETIs making cero, one, two or three contacts as a function of
   galactocentric distance.}
   \label{F_res_5}
\end{figure}

@@

\begin{figure*}
   \centering
   \includegraphics[width=0.33\textwidth]{waiting_a_acum_log.png}%
   \includegraphics[width=0.33\textwidth]{waiting_a_acum_lin.png}%
   \includegraphics[width=0.33\textwidth]{waiting_a_dif.png}

   \includegraphics[width=0.33\textwidth]{waiting_s_acum_log.png}%
   \includegraphics[width=0.33\textwidth]{waiting_s_acum_lin.png}%
   \includegraphics[width=0.33\textwidth]{waiting_s_dif.png}

   \includegraphics[width=0.33\textwidth]{prob1_10k.png}%
   \includegraphics[width=0.33\textwidth]{prob1_40k.png}%
   \includegraphics[width=0.33\textwidth]{prob1_80k.png}

   \caption{Fraction of the CETIs that have made at least one contact  
   as a funtion of the elapsed time since the awakening, given that
   they make at least one contact on their lifetime.}
   \label{F_}
\end{figure*}

\begin{figure*}
   \centering
   \caption{}
   \label{F_}
\end{figure*}
